---
title: "Fortress runs data analysis v2"
output:
  html_notebook: default
---

### Goal
The goal of this analysis is to provide basis for a function to generate a realistic fortress room and enemies given the following parameters:

* Room level
* Player count
* Runestone levels


### Data load and preparation

```{r}
source(paste0("./fortressRunDataLoad.R"))
dataTrain <- groupedByRoomLevel[roomLevel>0]
dataToPredict <- data.table(roomLevel=1:20, difficulty=playerMultiplier * getSoloDifficultyForRoomLevel(1:20), difficultyBeforePlayerMultiplier=getSoloDifficultyForRoomLevel(1:20))

```


### Dataset size: 

```{r}
ggplot(groupedByRoomLevel, aes(x=roomLevel, y=nRuns)) + geom_bar(stat="identity") + ylab("Number of runs") + xlab("Room level") + theme_bw()
```



### Difficulty
When removing the player count multiplier (see [link](https://docs.google.com/spreadsheets/d/1jtBjdncxspRt51K048islZdEPTZ06yBKuZX7_MBzprI/edit#gid=0)), difficulty clearly scales quadratically with room number (for a single player):

```{r}
ggplot(groupedByRun[runestoneLevels==1], aes(x=roomLevel, y=difficultyBeforePlayerMultiplier)) + geom_point() + geom_line() +
  xlab("Room level") + ylab("Difficulty before player count multiplier") + theme_bw() + ggtitle("Difficulty before player count multiplier is clearly quadratic")
```




### Number of enemies (in relation to difficulty)
The following charts all use difficulty for the X axis. Hopefully this number alone can be used to describe the following characteristic of a fortress room: 

* Average number of enemies (elites count as 2)
* Average enemy level
* Average enemy difficulty (stars)
* Average proficiency

I explicitly use difficulty instead of a combination of runestone levels, player count and room level. 

For this graph, I count the number of elites as 2 enemies. 

I use the following equation to predict number of enemies for a room:
$$ numberEnemies = \alpha + \beta * sqrt(difficulty) $$

```{r}
modelNEnemies <- lm(meanNEnemies ~ I(sqrt(difficulty)), dataTrain)
summary(modelNEnemies)
(title <- paste0("let nEnemies = ", modelNEnemies$coefficients[[1]], " + ", modelNEnemies$coefficients[[2]],  " * Math.sqrt(difficulty);"))

ggplot(groupedByRoomLevel, aes(x=difficulty, y=meanNEnemies))  + 
  geom_point(aes(y=minNEnemies), color="red") + 
  geom_point(aes(y=maxNEnemies), color="red") + geom_point() + theme_bw() + xlab("difficulty") + ylab("Average number of enemies") + 
  geom_line(data=data.table(x=dataTrain$difficulty, y=predict(modelNEnemies, dataTrain)), aes(x=x, y=y))
```





### Average enemy level (in relation to difficulty)
Here, the picture is clearer. 
The average enemy level seems to be a root function in relation to difficulty (which would make it linear in relation to room level). 

I use the following equation to predict the average enemy level in a room: 
$ averageEnemyLevel = \alpha + \beta * averageRunestoneLevel + \gamma * roomLevel $


```{r}
modelAverageEnemyLevel <- lm(averageEnemyLevel ~ runestoneLevels + roomLevel, dataTrain) #

ggplot(groupedByRoomLevel, aes(x=roomLevel, y=averageEnemyLevel)) +
  geom_point() + xlab("Difficulty") + ylab("Average enemy level") + theme_bw() + xlab("Room level") + ylab("Mean number of enemies") +
  geom_line(data=data.table(x=dataTrain$roomLevel, y=predict(modelAverageEnemyLevel, dataTrain)), aes(x=x, y=y))
```





### Computing a difficulty "budget" per enemy
When generating a room one approach could be to compute a difficulty "budget" per enemy, which would translate to enemy difficulty and enemy level.

This [post](https://www.reddit.com/r/harrypotterwu/comments/csgsdd/all_about_combat_damage_what_i_know_or_i_think_i/?st=k0gijz3i&sh=acd204fd) suggests the following might hold:

$$ overallDifficulty \approx 2 * \sum enemyDifficulty * enemyLevel (1+isElite)$$

This relation seems to be a good approach for room levels > 7 but inaccurate for easier rooms (room levels <= 7).

The following chart shows how the factor 2 may be computed.
I thus use the following equation to compute a "normalization" factor:
$$ difficultyBudgetPerEnemyMultiplier = \alpha + \beta * exp(-roomLevel) $$
$$ normalizedDifficultyBudgetPerEnemy = overallDifficulty / (difficultyBudgetPerEnemyMultiplier * nEnemies) $$

```{r}
ggplot(groupedByRun, aes(x=as.factor(roomLevel), y=difficulty/sumProposedMultiplication)) + geom_boxplot() + ylim(c(0, NA)) +
  theme_bw() + xlab("Room level") + ylab("Difficulty / sum(enemyLevel*enemyDifficulty*(1+isElite))") 
```




# Average enemy difficulty (stars)
More data is needed here. 
The average difficulty seems strongly influenced by the number of enemies in the room. 

I use the following equation to compute an average enemy difficulty:
$$ averageEnemyDifficulty = normalizedDifficultyBudgetPerEnemy / averageEnemyLevel $$

```{r}
ggplot(groupedByRoomLevel, aes(x=difficulty, y=averageEnemyDifficulty)) + geom_point(aes(y=minAverageEnemyDifficulty), color="red") + geom_point(aes(y=maxAverageEnemyDifficulty), color="red") + 
  geom_point() + ylim(c(1,5)) + theme_bw()+ xlab("Difficulty") + ylab("Average enemy difficulty (stars)")

```

# Elite probability
I use a static probability value (10%) for each enemy to be an elite. This seems to be independent of difficulty / room level / etc. 



# Average proficiency
The current theory is that when doing a solo fortress run you will be proficient against a certain percentage of enemies. 
I have seen values between 50% and 60%.

This graph disputes that theory and shows that this percentage may depend on difficulty/room level and is not in fact constant. However, more data is needed to model this relation. 

I use the following equation to predict average proficiency: 
$$ averageProficiency = \alpha + \beta * roomLevel $$

```{r}

modelAverageProficiency <- lm(averageProficiency ~ roomLevel, dataTrain)
ggplot(groupedByRoomLevel, aes(x=roomLevel, y=averageProficiency)) + 
  geom_point() + 
  geom_line(data=data.table(x=dataTrain$roomLevel, y=predict(modelAverageProficiency, dataTrain)), aes(x=x, y=y)) +
  theme_bw() + xlab("Room level") + ylab("Average proficiency")
```




